Approximation as Differentiation: Notes

### 2025-05-19 notes/cmon-enriched.tex
CMon is itself semi-additive.

The $\CMon$-enriched Yoneda embedding preserves biproducts, where (as in any functor category) biproducts in
$\PSh_{\CMon}(\cat{C})$ are computed pointwise.

>>>>

\todo{Generalise to any monoidal closed $\mathscr{V}$ with biproducts?} The $\CMon$-enriched Yoneda embedding
preserves biproducts, where (as in any functor category) biproducts in $\PSh_{\CMon}(\cat{C})$ are computed
pointwise, and noting that $\CMon$ itself has biproducts.

### 2025-05-19 notes/cmon.tex
CMon is itself semi-additive.

\begin{definition}[Category $\CMon$]
Define $\CMon$ to be the category which has as objects $X$ all commutative monoids and as morphisms $f: X \to
Y$ all commutative monoid homomorphisms.
\end{definition}

>>>>

\begin{definition}[Category $\CMon$]
\label{def:cmon:cmon}
Define $\CMon$ to be the category which has as objects $X$ all commutative monoids and as morphisms $f: X \to
Y$ all commutative monoid homomorphisms.
\end{definition}
